Equations & R Code

### 2016-06-07 manuscript/manuscript.Rmd
adds perspective plots for cv and richness from four species storage effect model
adds new figure on diversity-stability relationship

\noindent where $\theta$ is the fraction of live biomass that dies and is recycled into the resource pool, $\nu$ is the fraction of the resource pool carried over from the previous year, and $R^+$ is a random resource pulse. Model parameters and notation are described in table 1.

\begin{centering}
\begin{table}
\caption{Definition of model states and parameters.}
\begin{tabular}{l l}
\hline
Parameter & Definition \\
\hline
$N$ & live biomass \\
$D$ & dormant biomass \\
$R$ & resource pool \\
$r$ & maximum per capita growth rate \\
$a$ & Hill function parameter \\
$b$ & Hill function parameter \\
$\epsilon$ & resource-to-biomass conversion efficiency \\
$\alpha$ & allocation fraction of live biomass to dormant biomass \\
$\gamma$ & dormant-to-live biomass transition fraction (variable) \\
$\eta$ & dormant biomass mortality rate \\
$\beta$ & live biomass survival rate \\
$\theta$ & resource recycling fraction \\
$\nu$ & resource carry-over fraction \\
\hline
\end{tabular}
\end{table}
\end{centering}

@@

### Model Simulations
For each coexistence mechanism (storage effect, relative nonlinearity), we ran model simulations at different levels of resource variance ($R_{\sigma^2}$), environmental cue variance ($\sigma_E$), and correlation of species responses to the environmental cue ($\rho$). 
We ran simulations for 100 'seasons' with 60 day growing seasons. 
We averaged biomass over the growing season.
After discarding an initial 20 seasons to reduce transient effects on our results, we calculated the stability of summed species biomass through time and species synchrony through time.
For storage effect simulations, species were equivalent in their ability to capture and assimilate the resource (*R*) but had different, depending on $\rho$, germination rates.
For relative nonlinearity simulations, species had equivalent germination rates ($\rho = 1$) but different resource acquisition functions (fig. 1).
We explored a limited set of parameter space where the storage effect and relative nonlinearity were operating simultaneously.
Within-season dynamics were solved given initial conditions using the package 'deSolve' [@Soetaert2010] in R [@Team2013].

@@

>>>>

\noindent where $\theta$ is the fraction of live biomass that dies and is recycled into the resource pool, $\nu$ is the fraction of the resource pool carried over from the previous year, and $R^+$ is a random resource pulse drawn from a log-normal distribution with mean $\mu(R^+)$ and standard deviation $\sigma(R^+)$. Model parameters and notation are described in table 1.

\begin{centering}
\begin{table}
\footnotesize
\caption{Default values of model parameters and their descriptions. Parameters that vary depending on the mode and strength of species coexistence or depending on species copmetive hierarchies are labeled as "variable" in parantheses. The dormant-to-live biomass transition fraction ($\gamma$) is a function of other parameters, so has no default value.}
\begin{tabular}{l l l}
\hline
Parameter & Description & Value \\
\hline
$r$ & maximum per capita growth rate & 1 (variable) \\
$a$ & Hill function rate parameter & 2 (variable) \\
$b$ & Hill function curvature parameter & 2.5 (variable) \\
$\epsilon$ & resource-to-biomass conversion efficiency & 0.5 \\
$\alpha$ & allocation fraction of live biomass to dormant biomass & 0.5 (variable) \\
$\gamma$ & dormant-to-live biomass transition fraction & -- \\
$\rho$ & correlation of species' response to the environment & 0 (variable) \\
$\sigma_E$ & variance of the environmental cue & 2 (variable) \\
$\eta$ & dormant biomass mortality rate & 0.1 \\
$\beta$ & live biomass survival rate & 0 \\
$\theta$ & resource recycling fraction & 0 \\
$\nu$ & resource carry-over fraction & 0 \\
$\mu(R^+)$ & mean annual resource pulse & 20 (non-log scale) \\
$\sigma(R^+)$ & standard deviation of annual resource pulse & 0 (variable) \\
\hline
\end{tabular}
\end{table}
\end{centering}

@@

### Model Simulations
For each coexistence mechanism (storage effect, relative nonlinearity), we ran model simulations at different levels of resource variance ($R_{\sigma^2}$), environmental cue variance ($\sigma_E$), and correlation of species responses to the environmental cue ($\rho$). 
We ran simulations for 100 'seasons' with 60 day growing seasons. 
We averaged biomass over the growing season.
After discarding an initial 20 seasons to reduce transient effects on our results, we calculated the stability of summed species biomass through time and species synchrony through time.
For storage effect simulations, species were equivalent in their ability to capture and assimilate the resource (*R*) but had different, depending on $\rho$, germination rates.
For relative nonlinearity simulations, species had equivalent germination rates ($\rho = 1$) but different resource acquisition functions (fig. 1).
We explored a limited set of parameter space where the storage effect and relative nonlinearity were operating simultaneously.
Within-season dynamics were solved given initial conditions using the package ``deSolve`` [@Soetaert2010] in ``R`` [@Team2013].

@@

\begin{figure}[!ht]
  \centering
      \includegraphics[width=3in]{./components/persp_plots_formatted.png}
  \caption{Variability of total community biomass (\emph{a}) and species richness (\emph{b}) as a function of the variance of the environmental cue ($\sigma^2_E$), and the correlation of species responses to the environment ($\rho$). }
\end{figure}

\begin{figure}[!ht]
  \centering
      \includegraphics{./components/diversity_stability_relationship.png}
  \caption{Variability of total community biomass as a function of the the number of coexisting species at different levels of correlations of species' responses to environmental conditions ($\rho$).}
\end{figure}
